Responsible Machine Learning Techniques\\\large{Interpretable Models, Post-hoc Explanation, and Discrimination Testing}

### 2019-12-14 article-information-2019.tex
more work on figures

\begin{figure}[H]
\centering
%\includegraphics[width=8cm]{img/}
\label{fig:sim_mgbm_loc}
\caption{Mean Tree SHAP values across quintiles for the three most important input features for $g^\text{MGBM}$ on the simulated test data.}
\end{figure}

@@

\begin{figure}[H]
\centering
%\includegraphics[width=8cm]{img/}
\label{fig:sim_xnn_loc}
\caption{Mean Deep SHAP values across quintiles for the three most important input features for $g^\text{XNN}$ on the simulated test data.}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=15cm]{img/sim_mgbm_loc.png}
\label{fig:sim_mgbm_loc}
\caption{Tree SHAP values for three observations across selected percentiles of $g^\text{MGBM}(\mathbf{X})$ for the simulated test data. Tree SHAP values are reported in the margin space, prior to the application of the logit link function.}
\end{figure}

@@

\begin{figure}[H]
\centering
%\includegraphics[width=8cm]{img/}
\label{fig:sim_xnn_loc}
\caption{Mean Deep SHAP values across quintiles for the three most important input features for $g^\text{XNN}$ on the simulated test data. Deep SHAP values are reported in the probability space, after the application of the logit link function.}
\end{figure}
